---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# ggmotif
add DNA sequence motifs to ggplot

Inspired by, and letters based on, seqLogo Bioconductor package.

Plots DNA sequence motif in ggplot2 framework.

Either create a standalone plot, or add a sequence logo at a specific position with a specific size into a ggplot.

```{r}
library(ggmotif)
```

```{r example_ggmotif_plot}
ggmotif_plot("ACGWRT") 
```

Can also use position frequency matrix instead of character string:

```{r example_ggmotif_plot2}
mat = Biostrings::consensusMatrix("ACGWRT")
mat

ggmotif_plot(mat) 
```

Or add a sequence logo at a specific position with a specific size into a ggplot.
```{r example_ggmotif}
ggplot(data.frame(x = 1:5,y =1:5),aes(x=x,y=y)) + geom_line() + 
  ggmotif("ACGWRT", x.pos = 5.1, y.pos = 5.1, ht = 0.2, wt = 0.2) + 
  ggmotif_scale() 

```



